Dissertation Manuscript

### 2024-04-22 paper.qmd
add docx version; fix igas figure text; re-render everything.

    <!-- <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;DOCX <small>(download)</small>
  </a> -->

>>>>

<a class="btn btn-warning btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
  <iconify-icon inline="" icon="fa6-solid:file-arrow-down"></iconify-icon> &ensp;docx <small>(download)</small>
  </a>
    <!-- <a class="btn btn-info btn-sm mb-1" target="_blank" href="/Manuscript/output/TG_Full_Dissertation.docx">
  <iconify-icon inline="" icon="fa6-solid:file-word"></iconify-icon> &ensp;DOCX <small>(download)</small>
  </a> -->
